Model-based variable selection for regression with highly correlated variables.

### 2014-05-06 www/article13.tex
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@568 edb9625f-4e0d-4859-8d74-9fd3b1da38cb
up
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/correg@569 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

		Variables in $\boldsymbol{X}_f$ are in the followings supposed to be independent Gaussian mixtures with at least two distinct components each.
	%Thus if one have some hypothesis on the distribution of some variables (exponentially distributed for example) it is possible to use it without impacting the model in other ways. %compute corresponding $\psi$ according to it. %and then improve the walk (will keep a structure only if it is really relevant).%and give it as an input of \textsc{CorReg} and then improve the efficiency of the algorithm (it will find a structure only if it is really relevant).
	We now have a full generative model.

@@

	We note $I_r$ the set of indices of endogenous variables in $\boldsymbol{X}$ (explained ones).
We also define $I_f=\{I_f^1,\dots,I_f^p \}$ the set of the sets of indices of exogenous covariates (explaining ones $=\boldsymbol{X}_f$) with $\forall j \notin I_r, I_f^j=\emptyset$. 
We see that $I_f$ defines the non-null coefficients in $\boldsymbol{\alpha}_j$ (each sub-regression can be very parsimonious).
Then we have the explicit structure characterized by $S=(I_f,I_r,p_f,p_r)$ where $p_r=|I_r|$, $\boldsymbol{p}_f=(p_f^1,\dots,p_f^{p_r})$ is the vector of the number of covariates in each sub-regression  and $p_f^j=|I_f^j|$, with $|.|$ the cardinal of an ensemble. Our running example is then described by $S= \left( \{ \{1,2\}\},\{3\},(2),(1)\right)$
\\
	 We suppose a hierarchical uniform {\it a priori} distribution $P(S)=P(I_f | \boldsymbol{p}_f,I_r,p_r)P(\boldsymbol{p}_f|I_r,p_r)P(I_r|p_r)P(p_r)$  instead of the simple uniform law on $S$ that is generally used and provides no penalty.
	 Thus we have :
		\begin{eqnarray}
		BIC_+(X|S)&=&BIC(X|S) -\ln(P(S)) \label{Bicstar}
	\end{eqnarray}		
	It increases penalty on complexity for $p_r<\frac{p}{2}$ and $p_f^j<\frac{p}{2}$ . Hence %when using $BIC*$ 
	this constraint on $\hat{p}_r$ and $\hat{p}_f^j$ is given in the research algorithm when the Hierarchical Uniform hypothesis is made instead of Uniform one in numerical experiments (section \ref{sectionsimul} and \ref{sectionrealcase}).
		$BIC_+$ does not change $BIC$ but only $P(S)$ so the properties of $BIC_+$ are the same as classical $BIC$ but we obtain better results when the constraints on the complexity are verified.  %With the Hierarchical Uniform hypothesis we maximize $\psi(\boldsymbol{X},S)\approx BIC + P(S)$.

>>>>

		Variables in $\boldsymbol{X}$ are in the followings supposed to be independent Gaussian mixtures with at least two distinct components each. 
	%Thus if one have some hypothesis on the distribution of some variables (exponentially distributed for example) it is possible to use it without impacting the model in other ways. %compute corresponding $\psi$ according to it. %and then improve the walk (will keep a structure only if it is really relevant).%and give it as an input of \textsc{CorReg} and then improve the efficiency of the algorithm (it will find a structure only if it is really relevant).
	We now have a full generative model.

@@

	We note $I_r$ the set of indices of endogenous variables in $\boldsymbol{X}$ (explained ones).
We also define $I_f=\{I_f^1,\dots,I_f^p \}$ the set of the sets of indices of exogenous covariates (explaining ones $=\boldsymbol{X}_f$) with $\forall j \notin I_r, I_f^j=\emptyset$. 
We see that $I_f$ defines the non-null coefficients in $\boldsymbol{\alpha}_j$ (each sub-regression can be very parsimonious).
Then we have the explicit structure characterized by $S=(I_f,I_r,p_f,p_r)$ where $p_r=|I_r|$, $\boldsymbol{p}_f=(p_f^1,\dots,p_f^{p_r})$ is the vector of the number of covariates in each sub-regression  and $p_f^j=|I_f^j|$, with $|.|$ the cardinal of an ensemble. Our running example is then described by $S= \left( \{ \{1,2\}\},\{3\},(2),(1)\right)$
\\
	 We suppose a hierarchical uniform {\it a priori} distribution $P(S)=P(I_f | \boldsymbol{p}_f,I_r,p_r)P(\boldsymbol{p}_f|I_r,p_r)P(I_r|p_r)P(p_r)$  instead of the simple uniform law on $S$ that is generally used and provides no penalty.
	 Thus we have :
		\begin{eqnarray}
		BIC_+(X|S)&=&BIC(X|S) -\ln(P(S)) \label{Bicstar}
	\end{eqnarray}		
	It increases penalty on complexity for $p_r\leq\frac{p}{2}$ and $p_f^j\leq\frac{p}{2}$ . Hence %when using $BIC*$ 
	this constraint on $\hat{p}_r$ and $\hat{p}_f^j$ is given in the research algorithm when the Hierarchical Uniform hypothesis is made instead of Uniform one in numerical experiments (section \ref{sectionsimul} and \ref{sectionrealcase}).
		$BIC_+$ does not change $BIC$ but only $P(S)$ so the properties of $BIC_+$ are the same as classical $BIC$ but we obtain better results when the constraints on the complexity are verified.  %With the Hierarchical Uniform hypothesis we maximize $\psi(\boldsymbol{X},S)\approx BIC + P(S)$.
